---
output:
  html_document:
    highlight: null
    css: style.css
    self_contained: no
    keep_md: true
---

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(stringr)

date <- "5/17/2018"
vendor <- "Papa Johns"
title <- "Cities, Collective Knowhow and Economic Development"
file_title <- "Prevalence Scaling and Variance
of Urban Phenomena"
short_title_n = 7
speaker <- "Andres Gomez"
department <- "Postdoctoral Fellow at the Growth Lab, Center for International Development"
university <- "Harvard University"
github_home <- "https://github.com/uchicago-computation-workshop"


```

```{r, echo=FALSE}
#Function to Shorten Title
small_title <- function(x, n=3) {
  ul <- unlist(strsplit(x, split = "\\s+"))[1:n]
  paste(ul,collapse=" ")
}

#Characters
unwanted_array = list(    'Š'='S', 'š'='s', 'Ž'='Z', 'ž'='z', 'À'='A', 'Á'='A', 'Â'='A', 'Ã'='A', 'Ä'='A', 'Å'='A', 'Æ'='A', 'Ç'='C', 'È'='E', 'É'='E',
                            'Ê'='E', 'Ë'='E', 'Ì'='I', 'Í'='I', 'Î'='I', 'Ï'='I', 'Ñ'='N', 'Ò'='O', 'Ó'='O', 'Ô'='O', 'Õ'='O', 'Ö'='O', 'Ø'='O', 'Ù'='U',
                            'Ú'='U', 'Û'='U', 'Ü'='U', 'Ý'='Y', 'Þ'='B', 'ß'='Ss', 'à'='a', 'á'='a', 'â'='a', 'ã'='a', 'ä'='a', 'å'='a', 'æ'='a', 'ç'='c',
                            'è'='e', 'é'='e', 'ê'='e', 'ë'='e', 'ì'='i', 'í'='i', 'î'='i', 'ï'='i', 'ð'='o', 'ñ'='n', 'ò'='o', 'ó'='o', 'ô'='o', 'õ'='o',
                            'ö'='o', 'ø'='o', 'ù'='u', 'ú'='u', 'û'='u', 'ý'='y', 'ý'='y', 'þ'='b', 'ÿ'='y' )


#Year
year <- substr(date, nchar(date)-4+1, nchar(date))

#Author Name
author_clean_lower <- str_replace_all(str_to_lower(speaker), " ", "_")

#Remove Unwanted Characters
out <- author_clean_lower
for(i in seq_along(unwanted_array))
    out <- gsub(names(unwanted_array)[i],unwanted_array[i],out)
author_clean <- out
author_lastname <- tail(strsplit(author_clean,split="_")[[1]],1)

#Repository Name
#repo = paste(year, author_clean, sep = "_")
repo = author_clean
issues_page <- paste(github_home, repo, "issues", sep="/")
repo_page <- paste(github_home, repo, sep="/")

#Create File Name Parts
short_title <- small_title(file_title, short_title_n)
paper_file <- paste(year, author_lastname, short_title, sep="  ")

#Clean Up File Name
punct <- '[]\\?!\"\'#$%&(){}+*/:;,._`|~\\[<=>@\\^-]'

#Remove Punctuation
lowered_name <- str_to_lower(paper_file)
stripped_name <- str_replace_all(lowered_name, punct, "")
cleaned_name <- str_replace_all(stripped_name, " ", "_")
cleaned_paper_file <- paste(cleaned_name, "pdf", sep=".")

#File Name Link
paper_link = paste(github_home, repo, "blob/master", cleaned_paper_file, sep="/"  )


#Clean Short Title
short_title_clean <- str_replace_all(short_title, punct, "")

```

<br>

<h3 class=pfblock-header> The Computational Social Science Workshop Presents </h3>

<h1 class=pfblock-header3> `r speaker` </h1>
<h3 class=pfblock-header3> `r department` </h3>
<h3 class=pfblock-header3> `r university` </h3>

<br><br>



<p class=pfblock-header3>The <a href="https://macss.uchicago.edu/content/computation-workshop"> Computational Social Science Workshop </a> at the University of Chicago cordially invites you to attend this week's talk:</p>

<br>

<div class=pfblock-header3>
<h2 class=pfblock-header>
  <a href="`r paper_link`" >`r title`</a>
</h2>

<br>
</div>

<p class=footertext2>

**Abstract:** The challenges of economic development have typically been framed at the national level. However, cross-city differences in socioeconomic indicators within countries are, in general, greater than the cross-country differences. Moreover, the majority of people today live in cities, and their urban milieu largely determines their welfare. Therefore, there is a strong motivation to have deep scientific understandings of the underlying reasons for the differences across cities. In my research, the notion of “collective knowhow” is pivotal to understanding this problem, and the coupling of the fields of Urban Scaling, Economic Complexity, and Cultural Evolution is a necessary step to develop a theory of collective knowhow and its connection to urban economic development. I will present some of my own efforts in addressing these challenges, and show (1) a parsimonious model to explain some of the differences across cities, and across urban phenomena within cities, (2) ongoing work about a formalism to track and predict the accumulation of collective knowhow, and (3) an overview of projects where we have applied these insights to promote urban economic development in Colombian cities.
</p>

<br>

<h4 class=pfblock-header3> Thursday, `r date` </h4>
<h4 class=pfblock-header3> 11:00am-12:20pm </h4>
<h4 class=pfblock-header3> Kent 120 </h4>

<br>

<p class=pfblock-header3>A light lunch will be provided by `r vendor`.</p>

<br><br>

<p class=footertext2>

**`r speaker`** is currently a postdoctoral fellow of the Growth Lab at the Center for International Development (CID) at Harvard University. Andres’ research is centered at understanding what cities are, how they work, and how come we observe wide differences in socioeconomic well-being across them. He holds a Ph.D. in Applied Mathematics from Arizona State University, a M.S. in Industrial Engineering and an undergraduate degree in Physics, both from La Universidad de los Andes. Since his doctoral studies, he has been part of the Cities, Scaling and Sustainability research group at the Santa Fe Institute. At CID, he is also part of the development team of the atlases of economic complexity for Colombia and Mexico. He has professional experience in the financial sector and public sector consulting.
</p>




<br><br>

---

<p class=footertext> The 2017-2018 <a href="https://macss.uchicago.edu/content/computation-workshop"> Computational Social Science Workshop </a> meets each Thursday from 11 a.m. to 12:20 p.m. in Kent 120. All interested faculty and graduate students are welcome.</p>

<p class=footertext>Students in the Masters of Computational Social Science program are expected to attend and join the discussion by posting a comment on the <a href="`r issues_page`"> issues page </a> of the <a href="`r repo_page`"> workshop's public repository on GitHub.</a> Further instructions are documented in the Computational Social Science Workshop's <a href="https://github.com/uchicago-computation-workshop/README"> README on Github.</a></p>
